Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
consistently use Peano Arithmetic

Before the Ackermann sublibrary was moved from the Goedel package repository to the \Hydras repository, the Goedel package had around 7,000 specification LOC and 38,000 proof LOC. Figure~\ref{fig:genealogy} and Table~\ref{tbl:loc} thus reveal that the seemingly large Coq formalization of G\"{o}del's incompleteness theorem can be considered as a modestly-sized proof on top of general libraries for, on the one hand, first-order logic, primitive recursive functions, and Peano arithmetic (Ackermann), and on the other hand, prime numbers and their properties (Pocklington).

>>>>

Before the Ackermann sublibrary was moved from the Goedel package repository to the \Hydras repository, the Goedel package had around 7,000 specification LOC and 38,000 proof LOC. Figure~\ref{fig:genealogy} and Table~\ref{tbl:loc} thus reveal that the seemingly large Coq formalization of G\"{o}del's incompleteness theorem can be considered as a modestly-sized proof on top of general libraries for, on the one hand, first-order logic, primitive recursive functions, and Peano Arithmetic (Ackermann), and on the other hand, prime numbers and their properties (Pocklington).
